\Title

### 2023-02-20 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

Now that this general framework has been explained, we can add some heuristics, based on neuroscientific observations, to constrain our model and its strategies for solving the task that is used to solve the ecological task described in section~\ref{sec:task}. Note that the general framework is similar to that presented in~\cite{grimaldi_learning_2022} and that, apart from the more complex task to solve and a deeper analysis of the results, these novel heuristics inspired by neuroscience are the main methodological differences with that previous study. In our simulations, we set the size of the kernels to $(21, 17, 17)$ and define as many classes as the number of motions (directions and velocities): $N_\class = 8 \times 3$. To avoid introducing biases in the directions, we apply a circular mask to the spatial dimensions of the kernels. First, we observed that moving images produced trajectories of ON and OFF spikes, and that these were present in both polarities arrangements. This is due to the fact that our whitened images have a symmetry in the luminance profiles, and an image with inverted contrast is indistinguishable. Since this arrangement of polarities is independent of speed, we added a mechanism that collects the linear values for the movie and the movie with the ON and OFF cells flipped, keeping only the maximum value for each voxel. This is similar to the computation done for complex cells in primary visual cortex.  Second, we included a prior in the motions that could be selected, as there is a prior in natural scenes for slow speeds~\citep{vacher_bayesian_2018}. Since we want to capture the possible convergence of the trajectories of the events converging on each voxel, we apply a mask to the spatiotemporal kernels so that the connectivity is limited by the delay: the smaller the delay, the smaller the radius of the circular mask that is applied (\seeFig{kernels} for an illustration). This is consistent with neuroscientific principles because, due to the limits of the conduction delay along horizontal connections, the synaptic delay is related, by physical principles, to the distance between the presynaptic neuron and the postsynaptic one.

% The second heuristics is based on the observation that biological neurons have a sparse spiking activity.  From this observation, we set an output firing rate for the layer of spiking neurons in order to make a sparse selection of the events at which the model makes a decision. It results in the selection of the coefficients with the maximum likelihood value. Therefore, we will only select a given proportion of the most active cells, which we set here to $0.1\%$ of all output voxels \note{change accordingly to the model's parameters}. This threshold was found using cross-validation and future work should automate how this may be determined for various datasets. Given a stimulus input, the model thus yields a spike output in the postsynaptic address space.
% \note{describe the heuristics inspired by neuroscience, remaining complex cells}
\note{describe how we compute accuracy}

@@

>>>>

Now that this general framework has been explained, we can add some heuristics, based on neuroscientific observations, to constrain our model and its strategies for solving the task that is used to solve the ecological task described in section~\ref{sec:task}. Note that the general framework is similar to that presented in~\cite{grimaldi_learning_2022} and that, apart from the more complex task to solve and a deeper analysis of the results, these novel heuristics inspired by neuroscience are the main methodological differences with that previous study. First, in our simulations, we set the size of the kernels to $(21, 17, 17)$ and define as many classes as the number of motions (directions and velocities): $N_\class = 8 \times 3$. To avoid introducing biases in the directions, we apply a circular mask to the spatial dimensions of the kernels. Furthermore, we included a prior in the motions that could be selected, as there is a prior in natural scenes for slow speeds~\citep{vacher_bayesian_2018}. Since we want to capture the possible convergence of the trajectories of the events converging on each voxel, we thus apply a mask to the spatiotemporal kernels such that the smaller the delay, the smaller the radius of the circular mask that is applied (\seeFig{kernels} for an illustration). This is consistent with neuroscientific principles because, due to the limits of the conduction delay along horizontal connections, the synaptic delay is related, by physical principles, to the distance between the presynaptic neuron and the postsynaptic one. Second, we observed that moving images produced trajectories of ON and OFF spikes, and that these were present in both polarities arrangements. This is due to the fact that our whitened images have a symmetry in the luminance profiles, and an image with inverted contrast is indistinguishable. Since this arrangement of polarities is independent of speed, we added a mechanism that collects the linear values for the movie and the movie with the ON and OFF cells flipped, keeping only the maximum value for each voxel. This is similar to the computation done for complex cells in primary visual cortex.

% The second heuristics is based on the observation that biological neurons have a sparse spiking activity.  From this observation, we set an output firing rate for the layer of spiking neurons in order to make a sparse selection of the events at which the model makes a decision. It results in the selection of the coefficients with the maximum likelihood value. Therefore, we will only select a given proportion of the most active cells, which we set here to $0.1\%$ of all output voxels \note{change accordingly to the model's parameters}. This threshold was found using cross-validation and future work should automate how this may be determined for various datasets. Given a stimulus input, the model thus yields a spike output in the postsynaptic address space.
% \note{describe the heuristics inspired by neuroscience, remaining complex cells}

@@

\note{describe how we compute accuracy}
